---
title: "Stockx - Shoes"
date: "January 4, 2017"
output: html_document
---

What can we do with the StockX shoe data? Well, let's see...

##Setting up the data
First, we'll read in the Excel file, skipping the first 7 lines.
```{r, warning=FALSE, message=FALSE}
library(gdata)

#Read in data
  df <- read.xls("http://datanerd.stockx.com/stockx-2016-jordan-NMD-resell-ROI-010317.xlsx", sheet = 2, skip=7, header = TRUE)

#What's in the data?
  colnames(df)
```

Now let's prep the data. We'll do a matrix expansion of the color attributes, the shoe models, and clean up on the numerics.
```{r, warning=FALSE, message=FALSE}
#clean
  df <- df[,1:13]
  
#Clean up numerics
  for(k in c(7:13)){
    df[,k] <- as.numeric(gsub("[^[:alnum:][:space:].]","", as.character(df[,k])))
  }
  df$log_retail <- log(df$Retail.Price)
  
  
#expand colorway into matrix
  #Set delimiter to commas
  df[,4] <- trimws(gsub("[[:punct:]]",", ", as.character(df[,4])))
  
  #Split by comma delimiter 
  colors <- strsplit(df$Colorway,",")
  uni <- unique(trimws(unlist(colors)))
  
  #Expand into matrix
  mat <- matrix(nrow = nrow(df), ncol=length(uni))
  mat2 <- as.data.frame(mat)
  colnames(mat2) <- uni
  for(k in 1:length(colors)){
    temp <- trimws(unlist(colors[k]))
    temp <- temp[temp!=""]
    for(i in 1:length(temp)){
      mat2[[temp[i]]][k] <- 1
    }
  }
  
  #Plug in zeros
  mat2[is.na(mat2)] <- 0

  #Expand model
  df <-cbind(df,mat2)
  df <- cbind(df,model.matrix( ~ Model. - 1, data=df ))

```

Now that the data is in the right shape, we can estimate which factors give the greatest sales lift for each Jordans and NMDs. The estimation strategy will follow a log-log form:

$$ log(Last Sale)_i = f(Color Way, Model, log(Retail Price), Total Market) $$

where $i$ is an index of brand. Essentially, we'll produce a model per brand. As the dimensions are are nearly $n x n$, it makes most sense to use a form of regularization to conduct feature selection.


```{r, warning=FALSE, message=FALSE}
#drop 
  df <- df[df$log_retail!=-Inf & log(df$Last.Sale)!=-Inf,]
  
#Split data
  jordans <- df[as.character(df$Jordan.NMD)=="Jordan",]
  nmd <- df[df$Jordan.NMD=="NMD",]
    
#models
  library(glmnet)
  library(DT)
  
  nike_fit <- cv.glmnet(as.matrix(jordans[,c(11,14:(ncol(jordans)-1))]), log(jordans$Last.Sale), type.measure = "mse", nfolds = 4)
  nike_coef <- coef(nike_fit, s = "lambda.min")
  
  adidas_fit = cv.glmnet(as.matrix(nmd[,c(11,14:(ncol(nmd)-1))]), log(nmd$Last.Sale), type.measure = "mse", nfolds = 4)
  adidas_coef <- coef(adidas_fit, s = "lambda.min")
  
#Consolidate results
  coef_result <- as.matrix(cbind(nike_coef, adidas_coef))
  coef_result <- as.data.frame(coef_result)
  coef_result <- coef_result[coef_result[,1]!=0 | coef_result[,2]!=0,]
  coef_result$names <- row.names(coef_result)
  colnames(coef_result) <- c("Jordans","NMDs", "Features")
  coef_result <- coef_result[,c(3,1,2)]
  datatable(coef_result)
  
#Model results
  par(mfrow=c(1,2))
  plot(adidas_fit, sub="NMDs error rate")
  plot(nike_fit, sub="Jordans error rate")
```


